Trans-dimensional Bayesian Inference and Nested Sampling

### 2015-02-02 Documents/Talk/content.tex
References

\begin{frame}[t]{Real projects}
\begin{itemize}
\item Magnetar bursts
\item Making probabilistic catalogs
\item Gravitational lens time delays in unresolved systems
\item Gravitational lens inversion
\item Modelling the progress of parallel Nested Sampling runs (!)
\end{itemize}
\end{frame}

\begin{frame}[t]{Software}
\begin{itemize}
\setlength{\itemsep}{20pt}
\item Diffusive Nested Sampling in C++
{\tt github.com/eggplantbren/DNest3}
\item Birth-death models in C++
{\tt github.com/eggplantbren/RJObject}
\item These are free software (GPLd).
\item The learning curve is steep (sorry) but I'm open to collaborations.
\end{itemize}
\end{frame}

>>>>

\begin{frame}[t]{References}
\begin{itemize}
\item Diffusive Nested Sampling (0912.2380)
\item Birth-death MCMC in DNS (1411.3921)
\item Radial Velocity Data (1501.06952)
\item Probabilistic Catalogs (1211.5805)
\item Magnetar Variability (1501.05251)
\end{itemize}
\end{frame}

\begin{frame}[t]{Software}
Everything I've discussed today is GPLd and is on Github.
\end{frame}
